Supplementary Materials to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2022-04-16 paper/pge_appendix.Rmd
use 'Supplementary Materials' in title

---
title: 'Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative
  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere'
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: dcpo_gender_roles.bib
biblio-style: apsr
linestretch: 1.1
output: 
    pdf_document:
        toc: true
header-includes:
      - \usepackage{float}
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{booktabs}
---

\renewcommand{\thepage}{A\arabic{page}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

>>>>

---
title: 'Supplementary Materials to Public Gender Egalitarianism: A Dataset of Dynamic Comparative
  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere'
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: dcpo_gender_roles.bib
biblio-style: apsr
linestretch: 1.1
output: 
    pdf_document:
        toc: true
header-includes:
      - \usepackage{float}
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{booktabs}
---

\renewcommand{\thepage}{S\arabic{page}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
